\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Updated Fiure 17 title

<!--bin1 = 22, bin2 = 17, b = 374, non_empty = 140-->
According to @fig-mnist-tri-proj (b), the non-linear structure observed in the \gD{} layout of PaCMAP (@fig-pacmap-author) is also visible when visualizing the model overlaid on the data space. This indicates that PaCMAP accurately captures the non-linear structure of the $10\text{-}D$ data. Additionally, the model shows a twisted pattern within the non-linear structure in $10\text{-}D$ space (@fig-mnist-tri-proj (c)), which is an additional pattern not visible in the \gD{} representation (@fig-pacmap-author). Furthermore, as shown in @fig-mnist-tri-proj (d), some long edges exist in the $10\text{-}D$ space that are not recognized as long edges in the \gD{} representation. However, PaCMAP provides a reasonable \gD{} representation of MNIST digit 1 data, as it preserves the non-linear structure present in the $10\text{-}D$ data.

```{r}
#| label: mnist-model-proj

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "Model in \\gD{}, on the PaCMAP layout, and three views of the fit in projections from $10\\text{-}D$, for the digit 1 of MNIST data ($a_1 = 0.062$, $b = 285 \\  (19, \ 15)$, $m = 109$, and benchmark value to remove large edges is $0.108$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/zcg_GXBmqjA>)."

>>>>

PaCMAP provides a reasonable \gD{} representation of MNIST digit 1 data, as it preserves the non-linear structure present in the $10\text{-}D$ data (@fig-mnist-tri-proj). Furthermore, shows some quirks when visualizing the *model-in-the-data-space* (@fig-mnist-tri-proj).

<!-- According to @fig-mnist-tri-proj (b), the non-linear structure observed in the \gD{} layout of PaCMAP (@fig-pacmap-author) is also visible when visualizing the model overlaid on the data space. This indicates that PaCMAP accurately captures the non-linear structure of the $10\text{-}D$ data. Additionally, the model shows a twisted pattern within the non-linear structure in $10\text{-}D$ space (@fig-mnist-tri-proj (c)), which is an additional pattern not visible in the \gD{} representation (@fig-pacmap-author). Furthermore, as shown in @fig-mnist-tri-proj (d), some long edges exist in the $10\text{-}D$ space that are not recognized as long edges in the \gD{} representation. However, PaCMAP provides a reasonable \gD{} representation of MNIST digit 1 data, as it preserves the non-linear structure present in the $10\text{-}D$ data.  -->

<!--bin1 = 22, bin2 = 17, b = 374, non_empty = 140-->
```{r}
#| label: mnist-model-proj

@@

<!--add langevitour screenshots and youtube animation link-->
```{r}
#| label: fig-mnist-tri-proj
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "Model in \\gD{}, on the PaCMAP layout (a), and three views (b, c, d) of the fit in projections from $10\\text{-}D$, for the digit 1 of MNIST data ($a_1 = 0.062$, $b = 285 \\  (19, \ 15)$, $m = 109$, and benchmark value to remove large edges is $0.108$). (b) The non-linear structure observed in the \\gD{} layout of PaCMAP (@fig-pacmap-author) is also visible when visualizing the model overlaid on the data space. This indicates that PaCMAP accurately captures the non-linear structure of the $10\\text{-}D$ data. (c) the model shows a twisted pattern within the non-linear structure in $10\\text{-}D$ space, which is an additional pattern not visible in the \\gD{} representation (@fig-pacmap-author). (d) some long edges exist in the $10\\text{-}D$ space that are not recognized as long edges in the \\gD{} representation. The full video is available at <https://youtu.be/zcg_GXBmqjA>."

### 2024-08-26 paper.tex
Updated Fiure 17 title

According to Figure~\ref{fig-mnist-tri-proj} (b), the non-linear
structure observed in the \gD{} layout of PaCMAP
(Figure~\ref{fig-pacmap-author}) is also visible when visualizing the
model overlaid on the data space. This indicates that PaCMAP accurately
captures the non-linear structure of the \(10\text{-}D\) data.
Additionally, the model shows a twisted pattern within the non-linear
structure in \(10\text{-}D\) space (Figure~\ref{fig-mnist-tri-proj}
(c)), which is an additional pattern not visible in the \gD{}
representation (Figure~\ref{fig-pacmap-author}). Furthermore, as shown
in Figure~\ref{fig-mnist-tri-proj} (d), some long edges exist in the
\(10\text{-}D\) space that are not recognized as long edges in the \gD{}
representation. However, PaCMAP provides a reasonable \gD{}
representation of MNIST digit 1 data, as it preserves the non-linear
structure present in the \(10\text{-}D\) data.

@@

\caption{\label{fig-mnist-tri-proj}Model in \gD{}, on the PaCMAP layout,
and three views of the fit in projections from \(10\text{-}D\), for the
digit 1 of MNIST data (\(a_1 = 0.062\), \(b = 285 \  (19,  15)\),
\(m = 109\), and benchmark value to remove large edges is \(0.108\)).
(The \textbf{langevitour} software is used to view the data with a tour,
and the full video is available at \url{https://youtu.be/zcg_GXBmqjA}).}

>>>>

PaCMAP provides a reasonable \gD{} representation of MNIST digit 1 data,
as it preserves the non-linear structure present in the \(10\text{-}D\)
data (Figure~\ref{fig-mnist-tri-proj}). Furthermore, shows some quirks
when visualizing the \emph{model-in-the-data-space}
(Figure~\ref{fig-mnist-tri-proj}).

@@

\caption{\label{fig-mnist-tri-proj}Model in \gD{}, on the PaCMAP layout
(a), and three views (b, c, d) of the fit in projections from
\(10\text{-}D\), for the digit 1 of MNIST data (\(a_1 = 0.062\),
\(b = 285 \  (19,  15)\), \(m = 109\), and benchmark value to remove
large edges is \(0.108\)). (b) The non-linear structure observed in the
\gD{} layout of PaCMAP (Figure~\ref{fig-pacmap-author}) is also visible
when visualizing the model overlaid on the data space. This indicates
that PaCMAP accurately captures the non-linear structure of the
\(10\text{-}D\) data. (c) the model shows a twisted pattern within the
non-linear structure in \(10\text{-}D\) space, which is an additional
pattern not visible in the \gD{} representation
(Figure~\ref{fig-pacmap-author}). (d) some long edges exist in the
\(10\text{-}D\) space that are not recognized as long edges in the \gD{}
representation. The full video is available at
\url{https://youtu.be/zcg_GXBmqjA}.}
